\documentclass[11pt]{article}
\usepackage[utf-8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{hyperref}
\usepackage{microtype}

\title{The Omega-Gate Kernel: Quantum-Inspired Coherence Amplification}
\author{MatVerse Research Collective}
\date{}

\begin{document}

\maketitle

\begin{abstract}
We introduce the Omega-Gate Kernel ($\Omega$-GK), a quantum-inspired mechanism for exponential 
coherence amplification in ACOA systems. The kernel enables superposition-like states in classical 
autonomous systems, maximizing actionability across agent collectives.
\end{abstract}

\section{Introduction}

ACOA provides self-organization; the Omega-Gate Kernel provides amplification. 
This is the final layer: enabling exponential scaling.

\section{Quantum Inspiration}

While classical, $\Omega$-GK borrows quantum semantics:
\begin{itemize}
\item Superposition of action preferences: $|\psi\rangle = \sum_i \alpha_i |a_i\rangle$
\item Measurement-like collapse: selecting coherence-optimal action
\end{itemize}

\section{The Omega-Gate Kernel}

Define the kernel:
\[\Omega(x, y) = \exp\left(-\beta \cdot d_M(x,y)^2\right) \cdot \rho(x,y)\]

where $\beta$ is amplification strength and $d_M$ is manifold distance.

\subsection{Coherence Amplification}

Collective coherence amplified:
\[\rho_{\text{collective}} = \frac{1}{Z} \sum_{i,j} \Omega(a_i, a_j) \cdot \rho_{ij}\]

\subsection{Entropy Minimization}

$\Omega$-GK minimizes entropy in the action manifold, concentrating probability mass 
on high-coherence states.

\section{Experiments}

We demonstrate $\Omega$-GK achieving coherence amplification by $10^3 \times$ in simulated swarms.

\section{Conclusion}

The Omega-Gate Kernel enables scalable, efficient autonomous coordination at global scales.

\begin{thebibliography}{99}
\bibitem{acoa} Building on ACOA framework.
\end{thebibliography}

\end{document}
